### 2021-02-15 introduction.tex
Add a paragraph in Introduction
Add a todo

@@

>>>>

Modern \gls{fol} \glspl{atp}, such as Vampire, E or SPASS,
solve \gls{fol} problems by iteratively applying the inference rules of superposition calculus.
Literal selection and equation orienting are employed to limit the ... while preserving the refutation completeness.
Both literal selection and equation orienting are determined by \gls{sot}.

@@

\todo[inline,author=FB]{Mention contributions explicitly.}
